prolfqua - R-package for Analysing Proteomics Label Free Quantification Experiments

### 2022-02-07 inst/MyArticle/MergePoster.Rmd
adding references to introduction

Label-Free Quantification (LFQ) Proteomics Experiments enable monitoring relative abundances of thousands of proteins in biological samples. For most studies, parallel designs with a single explanatory variable are used, e.g., treatment vs. control. More recently, more complex experimental designs are implemented with increasing numbers of samples, i.e., factorial designs and longitudinal studies (time series), sometimes with repeated measurements on the same subject [...]. The obtained data can be modeled using linear fixed, mixed, or random-effects models [@Bates2015FittingJSS]. Based on these models, tests can be applied to examine whether a factor or interactions are significant, or differences between factor levels can be estimated, and their significance tested.  Proteins can be ordered or grouped using the estimated fold-change, t-statistics, scaled p-value, or false discovery rate (FDR) and then subjected to gene set enrichment or over-representation analysis [...] or validation experiments.

>>>>

Label-Free Quantification (LFQ) Proteomics Experiments enable monitoring relative abundances of thousands of proteins in biological samples. For most studies, parallel group designs are used, e.g., treatment vs. control are used[cite]. More recently, more complex experimental designs are implemented with increasing numbers of samples, i.e., factorial designs and longitudinal studies (time series), sometimes with repeated measurements on the same subject[cite]. The obtained data can be modeled using linear fixed, mixed, or random-effects models [@Bates2015FittingJSS]. Based on these models, tests can be applied to examine whether a factor or interactions are significant, or differences between factor levels can be estimated, and their significance tested.  Proteins can be ordered or grouped using the estimated fold-change, t-statistics, scaled p-value, or false discovery rate (FDR) and then subjected to gene set enrichment or over-representation analysis [...] or validation experiments.
